Main Analyses

### 2016-02-26 Rmd/figures.Rmd
Near final figures for main text done after revision to Fig 1 and 3, and new Figure 4 made. Model rerun for 100% yield gap closure on existing land.

# Main Analyses

@@

# gaps 
cp <- c("maize" = 2912004, "soy" = 203732)  # current production
gapper <- function(cp, gaps, pct) ((((cp * gaps) - cp) * pct) + cp) / cp
mzgap <- 4.43 / 2.3 
soygap <- 3.4 / 2
g <- gapper(cp, c(mzgap, soygap), 0.25)  # assume 50% closed on current land
targ <- c("maize" = 3, "soy" = 9)  # targets given g
targs <- targets(targ, cp, g)

@@

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
crops <- c("maize", "soy", "maize/soy")
# plot(1:10, pch = 20, cex = 4, col = "gold2")
# plot(mzsoyr, col = c("grey", "goldenrod", "green4", "orange"))
imp_plot2(mzsoyr, i1, p_figures, "ideal_yield", "", crops, 1, TRUE, 
         c("gold2", "green3", "orange"))

@@

```{r, eval = FALSE}
load(fp(p_out, "mainresults1702.rda"))
```

@@

### Figure 1
```{r, eval = FALSE}
# select out results for "pure" cases (weight = 1)
cnames <- c("Y", "C", "BD", "COST")
pure <- sapply(cnames, function(x) which(round(ybdc$both$params[, x], 4) == 1))

@@

# Jaccard Index of overlaps
rs_over_a <- sapply(1:length(rs_over), function(x) { # x <- 4
  sapply(1:2, function(y) {  # y <- 3
    r <- rs_over[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
pms2b$JS <- round(rs_over_a[2, ] / colSums(rs_over_a), 3)

@@

# select out corresponding impact statistics, summarize
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) conv_stats[[x]])

# Plot setup
m1 <- do.call(cbind, lapply(1:4, function(x) matrix(rep(x, 35), 5, 7)))
m2 <- matrix(rep(5, 20), 4, 5)
m3 <- do.call(cbind, lapply(6:12, function(x) matrix(rep(x, 12), 4, 3)))
lmat <- rbind(m1, cbind(rep(5, 4), m2, m3, rep(13, 4)))

# plot(1:10, ylab = ylabs[2])
# ylabs <- c("Jaccard Index", 
ylabs <- c(expression(paste("Converted area (", 10^5, " ", km^2, ")")), 
           "Hours", "C loss (Mt)", "Priority", "Intactness/priority",
           "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- c(10^5, 1, 100000, 1, 1, 1, 1)
ftits <- list("Y 100%", "C 100%", "Biod 100%", "Cost 100%")
leg <- c("Converted")

yaxes <- list(seq(0, 14, 2), seq(0, 7, 0.5),               
              seq(0, 1100, 100), seq(0, 0.12, 0.02), seq(0, 0.6, 0.1), 
              seq(0, 1, 0.1), seq(0, 6500, 500))
bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
                  cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))

# plot
tiff(fp(p_figures, "single_priorities2.tif"), height = 3.5, width = 7, 
     units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
for(i in 1:4) { # i <- 1
  imp_plot2(rs2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}

# impact plots
mgp <- c(1.6, 0.25, 0)
par(mar = c(4, 3, 0, 0))
with(pms2b, {
  plot(NND, JS, col = cols_tr[c(2, 3, 3, 4, 4, 4)], pch = 16, cex = 1.5, 
       axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.3))
  points(NND, JS, col = cols_tr[c(1, 1, 2, 1, 2, 3)], pch = 20, cex = 1)
  axis(1, at = seq(0, 230, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
  axis(2, at = seq(0, 0.3, 0.05), cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
  mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
  mtext(text = "Jaccard Index", side = 2, line = 1.25, cex = 0.45)
})
mgp <- c(1, 0.25, 0)
for(i in 1:7) {
  v <- impsr[[i]] / yscale[i]
  b <- barplot(impsr[[i]] / yscale[i], las = 2,  col = cols_tr, 
               mgp = c(1.5, 0.25, 0), tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = 0.5,
               cex.lab = 0.7)
  axis(2, at = yaxes[[i]], cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
}
dev.off()

@@

# heat maps
implist <- list(ycost$both, bdc$both)
load(full_path(set_base_path(), paste0("external/data/ZA/parks_roads.rda")))
pacols <- c("transparent", "grey85", "grey75")
png(full_path(p_figures, "ycost-bdc-heat.png"), height = 400, width = 900)
par(mfrow = c(1, 2), oma = c(0, 0, 0, 2))
for(i in 1:2) {
  par(mar = c(1, 1, 1, 4))
  plot(zambia, col = "grey90", border = "transparent")
  ir <- implist[[i]]$heat
  ir[ir == 0] <- NA
  plot(ir, col = rev(heat.colors(20)), add = TRUE, )
  plot(pas[pas@data$type == "gma", ], add = TRUE, col = pacols[2],
       border = FALSE)
  plot(pas[pas@data$type == "npark", ], add = TRUE, col = pacols[3],
       border = FALSE)
  plot(roads, add = TRUE, lwd = 0.1, col = "grey")
}
dev.off()

@@

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, fp(p_out, ybdc$both$bcode))

@@

dfunc <- function(x, y) 100 - y / x * 100
stnms <- names(cstats)[-1]
imp_pct <- cstats[, lapply(stnms, function(x) {
  dfunc(minmaxstats[[x]][2], get(x))
})]
setnames(imp_pct, stnms)

# plot(imp_pct$tot_C, imp_pct$conv_area, type = "l", xlab = "", ylab = "", 
#      axes = FALSE)        # xaxs = "r", yaxs = "r")

sctab <- do.call(rbind, scens) * 100
cx <- 0.7
lcols <- c("black", "red", "blue")
imp_pct[, {
  png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
      units = "in", res = 300)
  par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
  plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
       axes = FALSE, ylim = c(0, 65), xlim = c(2, 12))#, xaxs = "r", yaxs = "r")
  lines(conv_area, int_prior, col = "red")
  lines(conv_area, mu_cost, col = "blue")
  axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% land savings", side = 1, line = 1, cex = cx)
  mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
  inms <- c("tot_C", "int_prior", "mu_cost")
  for(i in 1:length(inms)) {
    text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
         cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
    text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
         offset = i * 0.15 - 0.2, col = lcols[i])
  }
  legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
         text.col = lcols, col = lcols, bty = "n", lty = 1)
  dev.off()
}]

fnames <- fp(fp(p_out, ybdc$both$bcode), 
             imp_sorter(fp(p_out, ybdc$both$bcode), inds = pind))
scens_r <- lapply(fnames, function(x) {  # x <- pind[[1]]
  print(x)
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})

scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
names(scens_rs2) <- paste0("w", 1:length(scens_rs2))

pms2b <- do.call(rbind.data.frame, lapply(2:6, function(x) {
  a <- rep(0, 6)
  a[c(1, x)] <- 1
  a
}))
colnames(pms2b) <- paste0("Var", 1:ncol(pms2b))
pms2b$cl <- c("W010", "W020", "W030", "W040", "W050")
rownames(pms2b) <- 1:5

# pairwise overlaps
scens_over <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
  calc(stack(scens_rs2[which(pms2b[x, ] == 1)]), sum)
})
names(scens_over) <- pms2b$cl

# Jaccard Index of overlaps
scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
  sapply(1:2, function(y) {  # y <- 3
    r <- scens_over[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
pms2b$JS <- round(scens_over_a[2, ] / colSums(scens_over_a), 3)

# calculate nearest neighbor distance between each version, using spatstat 
# nncross
zam_owin <- owin(xrange = bbox(zambia)[1, ], yrange = bbox(zambia)[2, ],
                 unitname = "meter")
which1 <- function(x) x == 1  # selector function for r to xy
scenover_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 4
  print(x)
  ind <- which(pms2b[x, 1:6] == 1)
  rl <- scens_rs2[ind]
  rxy <- lapply(rl, function(x) rasterToPoints(x, fun = which1))
  pps <- lapply(rxy, function(x) {
    ppp(x = x[, 1], y = x[, 2], window = zam_owin)
  })
  # reorder to find which has most points, to put that in as X
  reord <- sort(sapply(pps, function(x) x$n), decreasing = TRUE)
  ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
})
pms2b$NND <- round(sapply(scenover_nn, function(x) mean(x$dist))) / 1000

# plot(scens_rs2[[1]] + scens_rs2[[2]])
# check
# round(sapply(scens_rs2, function(x) {
#   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# }))
# cstats$conv_area

# pms <- list(c(1, 2), c(1, 3), c(1, 4), c(1, 5))
# pms <- expand.grid(rep(list(0:1), 5))[-1, ]  # logic grid

# rasters showing overlap as weight is progressively put on C and BD
scens_over2 <- lapply(2:6, function(x) scens_rs2[[1]] + scens_rs2[[x]] * 2)

# # overlap areas
# scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
#   sapply(1:3, function(y) {  # y <- 3
#     r <- scens_over[[x]] == y
#     # plot(r)
#     round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
#   })
# })
# colSums(scens_over_a[c(2, 3), ])
# over_cols <- sapply(seq(0, 0.4, 0.1), function(x) rgb(1 - x, 0, x))
# par(mar = c(0, 0, 0, 0))
# plot(1:3, pch = 20, col = rgb(1, 0, 1))
# plot(zambia)

# cols <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0.75, 0, 0.75))
# cols <- c("red", "blue", "gold")
bluecols <- sapply(c(1, 0.75, 0.5, 0.25, 0), function(x) rgb(0, x, 1))
bluecols[5] <- rgb(0.4, 0, 1)
cols <- sapply(1:length(bluecols), function(x) c("red", bluecols[x], "gold"))
plot(1:ncol(cols), pch = 20, col = cols[2, ], cex = 20)
ftits <- list("Y 90% C 5% Biod 5% Cost 0%",
              "Y 80% C 10% Biod 10% Cost 0%",
              "Y 70% C 15% Biod 15% Cost 0%",
              "Y 60% C 20% Biod 20% Cost 0%", 
              "Y 50% C 25% Biod 25% Cost 0%")
leg <- c("Y", "YCBd", "Y + YCBd")

tiff(fp(p_figures, "changing_weights2.tif"), height = 3.5, width = 7, 
     units = "in", res = 300)
par(mfrow = c(2, 3), oma = c(0, 0, 0, 1))
for(i in 1:5) { # i <- 1
  # map
  imp_plot2(scens_over2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[[i]], col = cols[, i], 
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = c(0, 0, 1, 0), titline = 0)
}
mgp <- c(1, 0.25, 0)
par(mar = c(3, 3, 1, 0))
with(pms2b, {
     plot(NND, JS, col = cols[2, ], pch = 16, cex = 1.5, 
          axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.4), 
          xlim = c(0, 180))
     points(NND, JS, col = cols[[1]][1], pch = 20, cex = 1)
     axis(1, at = seq(0, 180, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
          tcl = -0.2)
     axis(2, at = seq(0, 1, 0.1), cex.axis = 0.6, las = 2, mgp = mgp, 
          tcl = -0.2)
     mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
     mtext(text = "Jaccard Index", side = 2, line = 1, cex = 0.45)
})
dev.off()

#   # barplot
#   par(mar = c(5, 4, 3, 3))
#   overl <- scens_over_a[1:3, i][c(1, 3, 2)]
#   bp <- barplot(overl, las = 2, ylim = c(0, 12000),  
#                 col = cols[c(1, 3, 2)], mgp = c(1.5, 0.25, 0), tcl = -0.2, 
#                 ylab = expression(km^2), cex.axis = 0.6, cex.lab = 0.7)
#   axis(side = 1, at = bp, labels = leg, las = 2, 
#        mgp = c(1, 0.25, 0), tcl = -0.2, cex.axis = 0.6)
# }
# dev.off()

>>>>

# Figures

@@

# gaps 
cp <- c("maize" = 2912004, "soy" = 203732)  # current production
gapper <- function(cp, gaps, pct) ((((cp * gaps) - cp) * pct) + cp) / cp
mzgap <- 4.43 / 2.3 
soygap <- 3.4 / 2
g <- gapper(cp, c(mzgap, soygap), 1)  # assume 50% closed on current land
targ <- c("maize" = 4, "soy" = 10)  # targets given g
targs <- targets(targ, cp, g)

@@

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
crops <- c("maize", "soy", "maize/soy")
# plot(1:10, pch = 20, cex = 4, col = "gold2")
# plot(mzsoyr, col = c("grey", "goldenrod", "green4", "orange"))
imp_plot2(mzsoyr, i1, p_figures, "ideal_yield2", "", crops, 1.2, TRUE, 
         c("red", "blue1", "gold"))

@@

@@

### Figure 1
```{r, eval = FALSE}
load(fp(p_out, "mainresults2502.rda"))

# select out results for "pure" cases (weight = 1)
cnames <- c("Y", "C", "BD", "COST")
pure <- sapply(cnames, function(x) which(round(ybdc$both$params[, x], 4) == 1))

# check on dominated status
# ybdc$both$optitab[ind %in% 20:22]  # pure C not in optimum table
sic <- selected_impacts(20:22, fp(p_out, ybdc$both$bcode))
# (1 - sic$tot_C[1] / sic$tot_C[2]) * 100  # C is .07 more (dominated)
# probably because of over-shooting target
# ctst <- tradeoff_mod(prod_targ = targ, 
#                      cbetas = c("Y" = 0, "C" = 1, "BD" = 0, "COST" = 0),
#                      currprodmod = g)  
# selected_impacts2(ctst$impacts)  # correct one selected
# ybdc$both$params[20:22, ]

@@

# Jaccard Index of overlaps
rs_over_a <- sapply(1:length(rs_over), function(x) { # x <- 4
  sapply(1:2, function(y) {  # y <- 3
    r <- rs_over[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
pms2b$JS <- round(rs_over_a[2, ] / colSums(rs_over_a) * 100, 2)

@@

# select out corresponding impact statistics, summarize
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
# impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) conv_stats[[x]])
impsr <- lapply(c(2, 3, 8, 5), function(x) conv_stats[[x]])

# Plot setup
m1 <- do.call(cbind, lapply(1:4, function(x) matrix(rep(x, 35), 5, 7)))
m2 <- do.call(cbind, lapply(c(5, 8, 11, 14), function(x) {
  a <- matrix(rep(x, 16), 4, 4)
  b <- matrix(rep(x + 1, 6), 2, 3)
  cbind(a, rbind(b, b + 1))
}))

# m2 <- matrix(rep(5, 20), 4, 5)
# m3 <- do.call(cbind, lapply(6:12, function(x) matrix(rep(x, 12), 4, 3)))
# lmat <- rbind(m1, cbind(rep(5, 4), m2, m3, rep(13, 4)))
lmat <- rbind(m1, m2)

# plot(1:10, ylab = ylabs[2])
# ylabs <- c("Jaccard Index", 
ylabs <- c(expression(paste("Converted area (", 10^5, " ", km^2, ")")), 
           "Carbon loss (Mt)", #"Priority", 
           "Biodiversity Index", "Travel time (hours)")#,
           # "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- c(10^5, 100000, 1, 1)#, 1, 1, 1)
# ftits <- list("Y 100%", "C 100%", "Biod 100%", "Cost 100%")
ftits <- list("Maximize Yields", "Minimize Carbon Loss", 
              "Minimize Biodiversity Loss", "Minimize Travel Time")
# leg <- c("Converted")

yaxes <- list(seq(0, 16, 2), seq(0, 1200, 100), seq(0, 0.6, 0.1), 
              seq(0, 7, 1))#,               
              # seq(0, 1200, 100), #seq(0, 0.12, 0.02)), 
              #seq(0, 1, 0.1), seq(0, 6500, 500))
# bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
#                   cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))

# plot
# tiff(fp(p_figures, "single_priorities2.tif"), height = 3.5, width = 7, 
png(fp(p_figures, "single_priorities2.png"), height = 3.5, width = 7, 
    units = "in", res = 300)
# postscript(fp(p_figures, "single_priorities2.eps"), horizontal = FALSE, 
#            height = 3.5, width = 7)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
legtf <- c(FALSE, FALSE, FALSE, FALSE)
for(i in 1:4) { # i <- 1
  # par(mar = rep(0, 4))
  # plot(zambia, col = cols_tr[i])
  imp_plot2(rs2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = "", ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = legtf[i], hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}  
# impact plots
# mgp <- c(1.6, 0.25, 0)
# par(mar = c(4, 3, 0, 0))
# with(pms2b, {
#   plot(NND, JS, col = cols_tr[c(2, 3, 3, 4, 4, 4)], pch = 16, cex = 1.5, 
#        axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.3))
#   points(NND, JS, col = cols_tr[c(1, 1, 2, 1, 2, 3)], pch = 20, cex = 1)
#   axis(1, at = seq(0, 230, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
#        tcl = -0.2)
#   axis(2, at = seq(0, 0.3, 0.05), cex.axis = 0.6, las = 2, mgp = mgp, 
#        tcl = -0.2)
#   mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
#   mtext(text = "Jaccard Index", side = 2, line = 1.25, cex = 0.45)
# })
mgp <- c(1, 0.25, 0)
# for(i in 1:7) {
cx <- 0.6
for(i in 1:4) {
  v <- impsr[[i]] / yscale[i]
  par(mar = c(2, 3.5, 2, 0))
  b <- barplot(impsr[[i]] / yscale[i], las = 2, col = cols_tr, 
               mgp = c(1, 0.25, 0), tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = cx,
               cex.lab = 0.7)
  axis(2, at = yaxes[[i]], cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
  # mtext("Impacts", side = 3, cex = 1)
  ind <- which(pms2b[, paste0("Var", i)] == 1)
  with(pms2b[ind, ], {
    par(mar = c(0.5, 3, 2, 1), mgp = mgp)
    barplot(JS, col = cols_tr[-i], ylim = c(0, 30), yaxt = "n", 
            ylab = "% Overlap", cex.lab = cx)
    axis(2, at=seq(0, 30, 10), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    # mtext("Promixity", side = 3, cex = 1)
    par(mar = c(2, 3, 0.5, 1), mgp = mgp)
    barplot(NND, col = cols_tr[-i], ylim = c(0, 250), las = 2, yaxt = "n", 
            ylab = "", cex.lab = cx)
    axis(2, at=seq(0, 250, 50), cex.axis = cx, las = 2, mgp = mgp, tcl = -0.2)
    mtext("Average distance", side = 2, line = 1.72, cex = 0.4)
    mtext("to neighbor (km)", side = 2, line = 1.2, cex = 0.4)
  })
}
par(xpd = NA)
legx <- grconvertX(0.4, from = "ndc", to = "user")
legy <- grconvertY(0.5, from = "ndc", to = "user")
legend(x = legx, y = legy, legend = "Protected Areas", pch = 15, col = "grey75", 
       bty = "n", pt.cex = 3 * 0.6, cex = 1.5 * 0.6)
dev.off()

@@

# heat maps
# implist <- list(ycost$both, bdc$both)
# load(full_path(set_base_path(), paste0("external/data/ZA/parks_roads.rda")))
# pacols <- c("transparent", "grey85", "grey75")
# png(full_path(p_figures, "ycost-bdc-heat.png"), height = 400, width = 900)
# par(mfrow = c(1, 2), oma = c(0, 0, 0, 2))
# for(i in 1:2) {
#   par(mar = c(1, 1, 1, 4))
#   plot(zambia, col = "grey90", border = "transparent")
#   ir <- implist[[i]]$heat
#   ir[ir == 0] <- NA
#   plot(ir, col = rev(heat.colors(20)), add = TRUE, )
#   plot(pas[pas@data$type == "gma", ], add = TRUE, col = pacols[2],
#        border = FALSE)
#   plot(pas[pas@data$type == "npark", ], add = TRUE, col = pacols[3],
#        border = FALSE)
#   plot(roads, add = TRUE, lwd = 0.1, col = "grey")
# }
# dev.off()

@@

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, fp(p_out, ybdc$both$bcode))
cstats <- cstats[, .(iter, conv_area, tot_C, mu_cost, int_prior)]

@@

# cost is how much you pay relative to the best case
# savings is how much you gain relative to the worst case
dfunc <- function(x, y) (1 - y / x) * 100
# dfunc <- function(x, y) (x / y - 1) * 100
stnms <- names(cstats)[-1]
imp_pct <- cstats[, lapply(stnms, function(x) {
  mx <- minmaxstats[[x]][2]
  dfunc(mx, get(x))
})]
dfunc(minmaxstats[2, ], minmaxstats[1, ])  # maximum avoided cost

setnames(imp_pct, paste0(stnms, "p"))
imp_pct <- cbind("conv_km" = cstats[, conv_area] / 10^5, imp_pct)
ywgts <- do.call(rbind, scens)[, 1]
xwgts <- rowSums(do.call(rbind, scens)[, 2:3])
imp_pct <- cbind(cbind(ywgts, xwgts), cstats, imp_pct)

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
# lcols <- c("black", "red", "blue")
# imp_pct[, {
#   png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
#       units = "in", res = 300)
#   par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
#   plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
#   lines(conv_area, int_prior, col = "red")
#   lines(conv_area, mu_cost, col = "blue")
#   axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.2, mgp = c(1, 0.25, 0))
#   axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.15, mgp = c(1, 0.25, 0))
#   mtext("% land savings", side = 1, line = 1, cex = cx)
#   mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
#   inms <- c("tot_C", "int_prior", "mu_cost")
#   for(i in 1:length(inms)) {
#     text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
#          cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
#     text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
#          offset = i * 0.15 - 0.2, col = lcols[i])
#   }
#   legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
#          text.col = lcols, col = lcols, bty = "n", lty = 1)
imp_pct[, {
  png(fp(p_figures, "weight_impact3.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, int_priorp, col = cols_tr[3])
  lines(xwgts, mu_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel time"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

# fnames <- fp(fp(p_out, ybdc$both$bcode), 
#              imp_sorter(fp(p_out, ybdc$both$bcode), inds = pind))
# scens_r <- lapply(fnames, function(x) {  # x <- pind[[1]]
#   print(x)
#   DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
#   DTr <- dt_to_raster(DT, CRSobj)
# })
# 
# scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
# names(scens_rs2) <- paste0("w", 1:length(scens_rs2))
# 
# pms2b <- do.call(rbind.data.frame, lapply(2:6, function(x) {
#   a <- rep(0, 6)
#   a[c(1, x)] <- 1
#   a
# }))
# colnames(pms2b) <- paste0("Var", 1:ncol(pms2b))
# pms2b$cl <- c("W010", "W020", "W030", "W040", "W050")
# rownames(pms2b) <- 1:5
# 
# # pairwise overlaps
# scens_over <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
#   calc(stack(scens_rs2[which(pms2b[x, ] == 1)]), sum)
# })
# names(scens_over) <- pms2b$cl
# 
# # Jaccard Index of overlaps
# scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
#   sapply(1:2, function(y) {  # y <- 3
#     r <- scens_over[[x]] == y
#     round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
#   })
# })
# pms2b$JS <- round(scens_over_a[2, ] / colSums(scens_over_a), 3)
# 
# # calculate nearest neighbor distance between each version, using spatstat 
# # nncross
# zam_owin <- owin(xrange = bbox(zambia)[1, ], yrange = bbox(zambia)[2, ],
#                  unitname = "meter")
# which1 <- function(x) x == 1  # selector function for r to xy
# scenover_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 4
#   print(x)
#   ind <- which(pms2b[x, 1:6] == 1)
#   rl <- scens_rs2[ind]
#   rxy <- lapply(rl, function(x) rasterToPoints(x, fun = which1))
#   pps <- lapply(rxy, function(x) {
#     ppp(x = x[, 1], y = x[, 2], window = zam_owin)
#   })
#   # reorder to find which has most points, to put that in as X
#   reord <- sort(sapply(pps, function(x) x$n), decreasing = TRUE)
#   ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
# })
# pms2b$NND <- round(sapply(scenover_nn, function(x) mean(x$dist))) / 1000
# 
# cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# plot(1:4, cex = 3, pch = 20, col = cols_tr)
# 
# # plot(scens_rs2[[1]] + scens_rs2[[2]])
# # check
# # round(sapply(scens_rs2, function(x) {
# #   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# # }))
# # cstats$conv_area
# 
# # pms <- list(c(1, 2), c(1, 3), c(1, 4), c(1, 5))
# # pms <- expand.grid(rep(list(0:1), 5))[-1, ]  # logic grid
# 
# # rasters showing overlap as weight is progressively put on C and BD
# scens_over2 <- lapply(2:6, function(x) scens_rs2[[1]] + scens_rs2[[x]] * 2)
# 
# # # overlap areas
# # scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
# #   sapply(1:3, function(y) {  # y <- 3
# #     r <- scens_over[[x]] == y
# #     # plot(r)
# #     round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
# #   })
# # })
# # colSums(scens_over_a[c(2, 3), ])
# # over_cols <- sapply(seq(0, 0.4, 0.1), function(x) rgb(1 - x, 0, x))
# # par(mar = c(0, 0, 0, 0))
# # plot(1:3, pch = 20, col = rgb(1, 0, 1))
# # plot(zambia)
# 
# # cols <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0.75, 0, 0.75))
# # cols <- c("red", "blue", "gold")
# bluecols <- sapply(c(1, 0.75, 0.5, 0.25, 0), function(x) rgb(0, x, 1))
# bluecols[5] <- rgb(0.4, 0, 1)
# cols <- sapply(1:length(bluecols), function(x) c("red", bluecols[x], "gold"))
# plot(1:ncol(cols), pch = 20, col = cols[2, ], cex = 20)
# ftits <- list("Y 90% C 5% Biod 5% Cost 0%",
#               "Y 80% C 10% Biod 10% Cost 0%",
#               "Y 70% C 15% Biod 15% Cost 0%",
#               "Y 60% C 20% Biod 20% Cost 0%", 
#               "Y 50% C 25% Biod 25% Cost 0%")
# leg <- c("Y", "YCBd", "Y + YCBd")
#               
# tiff(fp(p_figures, "changing_weights2.tif"), height = 3.5, width = 7, 
#      units = "in", res = 300)
# par(mfrow = c(2, 3), oma = c(0, 0, 0, 1))
# for(i in 1:5) { # i <- 1
#   # map
#   imp_plot2(scens_over2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
#             crops = leg, ftitle = ftits[[i]], col = cols[, i], 
#             legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
#             marg = c(0, 0, 1, 0), titline = 0)
# }
# mgp <- c(1, 0.25, 0)
# par(mar = c(3, 3, 1, 0))
# with(pms2b, {
#      plot(NND, JS, col = cols[2, ], pch = 16, cex = 1.5, 
#           axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.4), 
#           xlim = c(0, 180))
#      points(NND, JS, col = cols[[1]][1], pch = 20, cex = 1)
#      axis(1, at = seq(0, 180, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
#           tcl = -0.2)
#      axis(2, at = seq(0, 1, 0.1), cex.axis = 0.6, las = 2, mgp = mgp, 
#           tcl = -0.2)
#      mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
#      mtext(text = "Jaccard Index", side = 2, line = 1, cex = 0.45)
# })
# dev.off()
# 
# 
# #   # barplot
# #   par(mar = c(5, 4, 3, 3))
# #   overl <- scens_over_a[1:3, i][c(1, 3, 2)]
# #   bp <- barplot(overl, las = 2, ylim = c(0, 12000),  
# #                 col = cols[c(1, 3, 2)], mgp = c(1.5, 0.25, 0), tcl = -0.2, 
# #                 ylab = expression(km^2), cex.axis = 0.6, cex.lab = 0.7)
